---
title: "STAT504_Project_Shi"
author: "Seraphina Shi"
date: "2/10/2020"
output: html_document
---

# 0. Import Libararies 
```{r}
#install.packages("tidyverse")
library(tidyverse)
```

# 1. load the dataset and keep the variables that we are interested in
```{r}
setwd("../STAT504_Final_Project")
rawdata <- read_csv("listings.csv")
rawdata <- rawdata[,c("price", "id", "name", "host_id", "host_name", "host_response_time", "host_response_rate", "neighbourhood_cleansed", "zipcode", "latitude", "longitude","property_type", "room_type", "accommodates", "bathrooms", "bedrooms", "beds", "amenities", "square_feet", "availability_365", "number_of_reviews", "review_scores_rating", "reviews_per_month", "instant_bookable", "cancellation_policy","minimum_nights", "cleaning_fee" )]
colnames(rawdata)
```


# 2. Data Cleaning  
## a. dropping duplicates  
```{r}
# checking duplicates
sum(duplicated(rawdata))  # there is no duplications in this data
```
## b. deal with missing values & any transformations?
```{r}
summary(rawdata) #check if there are any missing entries
```
  
Variables (host_response_time, host_response_rate, bathrooms, bedrooms, beds, square_feet, review_scores_rating, review_scores_value, reviews_per_month) has N/A values.  

```{r}
sample_n <- nrow(rawdata)
df <- rawdata
glimpse(df) #look variable names and types
```

### (1). clean "price", change from factor to dbl
```{r}
df$price <- suppressWarnings(as.double(substring(df$price, 2)))
```
```{r}
#check if price transformed properly
str(df$price)
summary(df$price) 
df$price[1:20]
rawdata$price[1:20] 
```
```{r}
# there is one NA in the price, check and replace it.
which(is.na(df$price)) 
rawdata$price[3123]
df$price[3123] = 1000.00
```
```{r}
summary(df$price)
```

### (2). Change id and host_id from int to fct
```{r}
df$id <- as.factor(df$id)
df$host_id <- as.factor(df$host_id)
```

### (3). clean host_response_time
```{r}
str(df$host_response_time)
```
```{r} 
df$host_response_time <- as.character(df$host_response_time)
str(df$host_response_time)
table(df$host_response_time)  
```
```{r}
df$host_response_time[df$host_response_time == ""] <- "0"
df$host_response_time[df$host_response_time == "N/A"] <- "0"
df$host_response_time[df$host_response_time == "within an hour"] <- "1"
df$host_response_time[df$host_response_time == "within a few hours"] <- "5"
df$host_response_time[df$host_response_time == "within a day"] <- "24"
df$host_response_time[df$host_response_time == "a few days or more"] <- "50"
df$host_response_time <- as.factor(df$host_response_time)
table(df$host_response_time)
```

### (4). clean host_response_rate
```{r}
str(df$host_response_rate)
table(df$host_response_rate)
```
```{r}
df$host_response_rate <- as.character(df$host_response_rate)
# clean N/A and missing entries
df$host_response_rate[df$host_response_rate==""] <- "0%"
df$host_response_rate[df$host_response_rate=="N/A"] <- "0%"  
# convert to numbers
df$host_response_rate = substr(df$host_response_rate,1,nchar(df$host_response_rate)-1)
df$host_response_rate <- as.numeric(df$host_response_rate)
summary(df$host_response_rate)
```

### (5) clean bathrooms, bedrooms, beds (fill the missing entries with 0)   

```{r}
df$bathrooms[is.na(df$bathrooms)] <- 0
df$bedrooms[is.na(df$bedrooms)] <- 0
df$beds[is.na(df$beds)] <- 0
summary(df$bathrooms)
summary(df$bedrooms)
summary(df$beds)
```


### (6) clean amenities
```{r}
df$amenities <- as.character(df$amenities)
```
```{r}
# Free Parking on Premises
parking <- rep(0, sample_n)
parking[str_detect(df$amenities, regex("Free Parking", ignore_case=T))] <- 1
parking <- as.factor(parking)
table(parking)
df <- cbind(df, parking)
```
```{r}
# Washer, Dryer 
washer <- rep(0,sample_n)
washer[str_detect(df$amenities, regex("Washer", ignore_case=T))] <- 1
washer <- as.factor(washer)
table(washer)
df <- cbind(df, washer)
```
```{r}
# 24-Hour Check-in
checkin <- rep(0,sample_n)
checkin[str_detect(df$amenities, regex("24-Hour Check-in", ignore_case=T))] <- 1
checkin <- as.factor(checkin)
table(checkin)
df <- cbind(df, checkin)
```
```{r}
# Pets Allowed
Pets_Allowed <- rep(0,sample_n)
Pets_Allowed[str_detect(df$amenities, regex("Pets Allowed", ignore_case=T))] <- 1
Pets_Allowed <- as.factor(Pets_Allowed)
table(Pets_Allowed)
df <- cbind(df, Pets_Allowed)
```

### (7) clean square_feet
```{r}
sum(is.na(df$square_feet))/sample_n
```
97.5% of observations do have the square feet, so we won't use this variable in our analysis. 

### (8) clean review_scores_rating (fill the missing entries with 0, and change to quantiles, then treat it as factors)
```{r}
df$review_scores_rating[is.na(df$review_scores_rating)] <- 0
table(df$review_scores_rating)
summary(df$review_scores_rating)
```
```{r}
i = 0
for (i in 1:length(df$review_scores_rating)) {
  if (df$review_scores_rating[i] < 87) {df$review_rating[i] <- "bad"
  } else 
  {
    if (df$review_scores_rating[i] >= 87 & df$review_scores_rating[i] < 95) {
      df$review_rating[i] <- "fair"
    } else 
    {if (df$review_scores_rating[i] >= 95 & df$review_scores_rating[i] < 98) {
      df$review_rating[i] <- "good"
    } else {df$review_rating[i] <- "excellent"}
    }}
  i = i + 1
  
}

table(df$review_rating)

```

### (9) clean reviews_per_month
```{r}
df$reviews_per_month[df$reviews_per_month == ""] <- 0

df$reviews_per_month[is.na(df$reviews_per_month) == TRUE] <- 0

summary(df$reviews_per_month)

```


# 3. Data visualization 
       outliers?
a. variable selection  
       plot variables  
       linear?
b. variables independent?  
       pair plots?  
       correlation between variables?  


# 4. Regression  
  model selection
